Layer based routing to obtain quality optimization of video streaming in the Future Internet

### 2012-12-11 paper/paper.tex
mja

We created the topology shown in Figure \ref{fig:topology}, on which we performed the experiments.

@@

An evaluation metric has to represent a value which is relevant to what we want to improve, which is why a measurement must:
\begin{itemize}
	\item represent the quality of the received video
	\item represent the performance of the network
	\item represent the impact on best effort traffic
\end{itemize}
To measure quality of the video we have chosen for the PSNR value of the received video compared to the raw footage. The higher the PSNR value, the better the frames were preserved during transfer. To measure the performance of the network we used the bitrate of all traffic. We also show the packet loss of best effort traffic caused by prioritizing the QoS flow...

\section{Conclusion}
The conclusion goes here.

>>>>

We created the topology shown in Figure \ref{fig:topology}, on which we performed the experiments.
Each link has a 1 Gb connection. The switches are running OpenVSwitch instead of the reference user-space switch, 
because Floodlight won't work with the reference user-space switch.

@@

To measure the quality of the video we chose the PSNR value of the received video compared to the raw footage. 
The higher the PSNR value, the better the frames were preserved during transfer. 
A base layer has a low PSNR value, and every extra enhancement layer that is also received, 
increases this value. %In Figure \ref{fig:psnr} we show the PSNR value as a function of time.
Unfortunately, we did not have enough time to obtain results.

\section{Conclusion}
In this paper we described a way to perform quality optimization of video streaming.
We do this by using HTTP adaptive streaming of an SVC encoded video stream, which is composed of a base layer and three enhancement layers.
Each layer is routed differently, depending on the required Quality of Service. 
The base layer is delivered as a lossless video stream. This means it is always delivered. It has the highest QoS priority.
The enhancement layers are considered lossy video streams, which means they may not always arrive, 
depending on the network load. We also implemented fast failure recovery. This means if a link fails, the routes get recalculated very fast, 
rendering an optimal performance.

In future work we will try to optimize the weights given to each link in the algorithm. 
This will give an even higher quality optimization.
